### 2016-08-04 Engine.tex
1.修改Verifacion部分(完成);2.修改自适应构造节点部分(完成)

\begin{enumerate}
\item Create a suffix set $SF$, and put each pattern of the pattern
  set into $SF$, where each pattern is regarded as a suffix of itself.
\item Compute the \emph{length of the shortest suffix} ($lss$) in
  $SF$. For each suffix in $SF$, remove its length-$lss$ prefix, and
  all the removed prefixes form a prefix set $PF$. Discard the
  repetitions in $PF$, and calculate $|PF|$ which refers to the
  \emph{number of distinct prefixes} ($ndp$).
\item Create a tree \emph{node} to hold the prefixes in $PF$. The
  \emph{node} is actually an index, in which each prefix serves as a
  key. The inner structure of the \emph{node} is constructed
  adaptively according to $ndp$ and $lss$ that have been computed in
  step 2.
\item Divide $SF$ by putting together all its suffixes who have the
  same prefix removed, to form a sub-suffix-set. Associate each
  sub-suffix-set with the corresponding prefix in the tree \emph{node}.
\item For each newly created sub-suffix-set in step 3, repeat the same
  procedure from step 2.
\end{enumerate}

@@

As stated in the filtering phase, once a suspicious position in the
text has been detected by the filter module, the verification module
checks that position for real pattern occurrences. In particular, for
such a suspicious position $i$, the engine searches a sequence of
substrings of the text, where the first substring starts at $i$, in
the corresponding nodes in AMT from the root. If the text successfully
matched a key that is marked as a pattern end in some node, a pattern
is declared to be found at position $i$. However, if there is a
mismatch or the searching goes beyond the leaves of AMT, the engine
forwards to the next position of the text and invokes the filter.

The pseudocode of verifying is shown in Algorithm
\ref{alg:matching}. Suppose $i$ is a suspicious position in the
text. The $m\_len$ is the total length of the successfully matched
sub-strings of the text. The $node$ points to the current matching
node in the AMT. In addition, since all the keys in a node have the
same length, the notation $key\_len(node)$ is used to denote the
length of the keys in $node$.

\begin{algorithm}
  \caption{Verification}\scriptsize
  \label{alg:matching}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A suspicious position $i$ in the text $T$\\
    The AMT built from the pattern set $P$\\
    \ENSURE ~~\\
    The patterns start at $i$ (if any)
    \STATE
    \STATE $m\_len \leftarrow 0$
    \STATE $node \leftarrow root$ of AMT
    \STATE
    \WHILE{$node \neq NULL$ and $\exists key \in node: key =
      T[i+m\_len, \, key\_len(node)]$}
    \STATE $m\_len \leftarrow m\_len + key\_len(node)$
    \IF{$key$ is marked as a pattern end}
    \STATE The pattern $T[i,\,m\_len]$ is found at position $i$
    \ENDIF
    \STATE $node \leftarrow$ The child of $node.key$
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{./eps/match}
  \caption{The matching round that searches patterns starting at
    position $i$ of the text.}
  \label{fig:matching}
\end{figure}

Next, an example is given in figure \ref{fig:matching} to illuminate
the verification for position $i$ of a given text string $T$, using
the AMT built in section \ref{subsec:amt}. The matching round starts
from the root of AMT: according to $key\_len(root)=2$, the same length
sub-string starting at position $i$ of $T$, which is $T[i,\,2]=aa$, is
taken to check whether it's one of the keys in root. The result is
that: $aa \in root$, and also $aa$ is marked as a pattern
end. Therefore the pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is
found at position $i$. Then the matching transfers to $node_1$, which
is the child node of $root.aa$.

At $node_1$, since $key\_len(node_1)=6$, the same length sub-string
$T[i+2,\,6]=e^6$, which appears following $T[i,\,2]$, is trying to
match with some key in $node_1$. The result is that: $e^6 \in node_1$
but it is not marked as a pattern end. Then the matching simply
transfers to $node_5$, which is the child of $node_1.e^6$.

At $node_5$, since the next sub-string $T[i+8,\,5]=u^5 \in node_5$ and
$u^5$ is marked as a pattern end, another pattern
$T[i,\,13]=a^2e^6u^5$ (actually $p_4$ in $P$) is found at position
$i$. Then the matching goes to the child of $node_5.u^5$, i.e.
$node_{10}$.

At $node_{10}$, since $T[i+13,\,4]=sscc \notin node_{10}$, the current
matching round for position $i$ terminates. The algorithm restarts a
new matching round for the next position $i+1$. Once all the positions
of the text have been checked, the whole algorithm terminates.

In our approach, each matching round actually corresponds to a
\textsf{matching path} in the AMT, whose tree nodes have been compared
with the text in the former matching process. In particular, the
matching path of the given example is:
$root \rightarrow node_1 \rightarrow node_5 \rightarrow node_{10}$,
witch is indicated by the dashed arrows in Figure \ref{fig:matching}.

@@

As stated in section \ref{subsec:amt}, each node of AMT has a specific
structure to hold the prefixes of a prefix set as the keys. The type
of the node structure is chosen adaptively according to the features
of the prefix set. Since all the keys in the prefix set have the same
length, the features of the prefix set can mainly be characterized by
two parameters: the \textsf{length} and \textsf{number} of the keys in
the prefix set. These two parameters are respectively symbolized by
$lss$ and $ndp$ in Section \ref{subsec:amt}.

In this work, three kinds of structures, i.e. \textsf{character map},
\textsf{string array} and \textsf{hash table} can be adopted for
prefix sets with different $lss$ and $ndp$ combinations. Next, the
detailed descriptions of them will be presented.

@@

Given a prefix set, if the length of keys is equal to 1 ($lss=1$),
i.e. each key in the prefix set is just a single character, we adopt
the space-efficient \textsf{character map} structure, which was
proposed by Leis \cite{Leis2013}, as the tree node. There are four
sub-types of character maps with different capacities for different
number of keys ($ndp$), where $1 \leq ndp \leq 256$.

@@

Figure \ref{fig:character map} illustrates the four sub-types of
character maps which are named according to their maximum
capacity. Instead of using an array of (\emph{key, child pointer})
pairs, the key part and the child pointer part are stored in the
separate arrays, which is able to keep the node information compact
while supporting efficient search.

\begin{itemize}
\item \textbf{Map 4} (for $1 \leq ndp \leq 4$): The smallest map type
  can store up to 4 keys. It uses an array of 4 entries for keys and
  another array of the same length for child pointers. The keys and
  child pointers are stored at corresponding positions in their
  arrays, and the keys are sorted according to their ACSII
  values. Once the target character is found in the key array, its
  child pointer can be located through the same position in the
  pointer array. Figure \ref{fig:character map} (a) shows a Map 4
  structure with three keys: $a$, $b$ and $c$, where the triangles
  with the keys inside represent the corresponding child nodes.

\item \textbf{Map 16} (for $5 \leq ndp \leq 16$): This map type is
  used for storing 5 to 16 keys. It has the similar structure as Map
  4, but both arrays have up to 16 entries. A target character can be
  retrieved efficiently by a binary search in the key array. Figure
  \ref{fig:character map} (b) shows a Map 16 structure with 14 keys:
  $a \sim n$.

\item \textbf{Map 48} (for $17 \leq ndp \leq 48$): As the number of
  keys increases, searching in the key array becomes
  expensive. Therefore, maps with more than 16 (but less than 49) keys
  do not store the keys explicitly. Instead, a 256-element
  \textsf{index array} is used, which can be directly indexed by the
  ASCII value of the target character. This array stores only the
  \textsf{array indexes} (small inters in the range of $[0,47]$) of
  another pointer array that contains up to 48 child pointers. In this
  way, the storage space can be saved comparing with storing pointers
  directly, because each array index only requires one byte. Figure
  \ref{fig:character map} (c) shows a Map 48 structure, where the
  ASCII values of $a$, $b$ and $c$ are 97, 98 and 99 respectively.

@@

For the sake of clarity, the pseudocode of searching in a node, whose
type is character map, is given in Algorithm \ref{alg:character map}.

\begin{algorithm}
  \caption{Searching in a node whose type is character map}\scriptsize
  \label{alg:character map}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is character map\\
    The target character $t\_ch$.
    \ENSURE ~~\\
    The child node of $node.t\_ch$ (possibly $NULL$).
    \STATE
    \STATE $count \leftarrow$ Number of keys in the character map
    \STATE
    \SWITCH{the sub-type of the character map}
    \CASE{\textsf{Map 4}}
    \FOR{$i \leftarrow 0$ to $count-1$}
    \IF{$keys[i]=t\_ch$}
    \RETURN $child\_pointers[i]$
    \ENDIF
    \ENDFOR
    \RETURN $NULL$
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 16}}
    \STATE $low \leftarrow 0, high \leftarrow count-1$
    \WHILE{$low \le high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_ch=keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_ch<keys[mid]$}
    \STATE $high \leftarrow mid-1$
    \ELSE
    \STATE $low \leftarrow mid+1$
    \ENDIF
    \ENDWHILE
    \RETURN $NULL$
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 48}}
    \IF{$index[t\_ch] \neq NULL$}
    \RETURN $child\_pointers[index[t\_ch]]$
    \ELSE
    \RETURN $NULL$
    \ENDIF
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 256}}
    \RETURN $child\_pointers[t\_ch]$
    \ENDCASE
    \ENDPWITCH
  \end{algorithmic}
\end{algorithm}

@@

For the prefix set whose length of keys is greater than 1 ($lss > 1$)
and the number of keys is not greater than 100 ($ndp \leq 100$), the
\textsf{string array} structure is constructed as a tree node. Similar
to the character map, the keys are stored in lexicographical order in
a separate key array of $ndp \times lss$ bytes, in which each key
takes $lss$ bytes. The child pointers are stored at the corresponding
positions in another pointer array of $8 \times ndp$ bytes, where each
pointer takes 8 bytes in a typical x86\_64 architecture. Figure
\ref{fig:string array} illustrates a string array structure holding
there keys: $aaa$, $bbb$ and $ccc$. The key and pointer arrays occupy
9 and 24 bytes respectively.

@@

For efficiency, if the number of keys is less than 5, a naive linear
search routine is used to search the target string in the key array;
otherwise, a more efficient (but complicated) binary search algorithm
is adopted.  The pseudocode of the searching in a node whose type is
string array is depicted in Algorithm \ref{alg:string array}, where we
use the notation $A \prec B$ to denote that string $A$ is
\textsf{lexicographically smaller} than string $B$. For the string
array whose number of keys is less than 5, the target string is
compared sequentially with the keys in the key array. If the target
string matched some key, return the child pointer at the corresponding
position in the pointer array; otherwise, return $NULL$. On the other
hand, if the number of keys is greater than 4, the target string is
searched by a binary search routine from the middle element of the key
array.

\begin{algorithm}
  \caption{Searching in a node whose type is string array}\scriptsize
  \label{alg:string array}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is string array; \\
    The target string $t\_str$.\\
    \ENSURE ~~\\
    The child node of $node.t\_str$ (possibly $NULL$).\\
    \STATE
    \STATE $count \leftarrow$ The number of keys in $node$
    \STATE
    \IF{$count < 5$}
    \STATE $i \leftarrow 0$
    \WHILE{$i < count$ and $keys[i] \prec t\_str$}
    \STATE $i \leftarrow i+1$
    \ENDWHILE
    \IF{$i < count$ and $keys[i]=t\_str$}
    \RETURN $child\_pointers[i]$
    \ELSE
    \RETURN $NULL$
    \ENDIF
    \ELSE
    \STATE $low \leftarrow 0$, $high \leftarrow count-1$
    \WHILE{$low \leq high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_str = keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_str < keys[mid]$}
    \STATE $high \leftarrow mid - 1$
    \ELSE
    \STATE $low \leftarrow mid + 1$
    \ENDIF
    \ENDWHILE
    \RETURN $NULL$
    \ENDIF
  \end{algorithmic}
\end{algorithm}

@@

For the prefix set whose number of keys is greater than 100 ($lss > 1$
and $ndp > 100$), searching in the string array structure becomes
inefficient even using a binary search. In this case, a more fast (but
heavy) data structure --- \textsf{hash table} is adopted to deal with
large number of keys. In this work, a hash table is an array of child
pointers with each pointer initialized to $NULL$, and we utilize a
\textsf{string hash function} which transforms a string to a positive
integer. It is worth noting that, the procedure of building a hash
table is directly based on the suffix set rather than the prefix set
which is the basis of building other structures.

@@

In particular, given a suffix set $SF$, the size of the hash table
(denoted by $table\_size$) is determined by $ndp$ and a given
\textsf{load factor} $lf$ (ratio of $ndp$ to $table\_size$), i.e.
$table\_size = \lceil ndp\,/\,lf \rceil$. For example, with the $ndp$
of 1000 and a load factor of $70\%$, the $table\_size$ is
$\lceil 1000/0.7 \rceil = 1429$. Note that, the $ndp$ here is defined
to be the number of distinct length-$lss$ prefixes of the suffixes in
$SF$, which is equal to the size of the prefix set derived from $SF$
(after removing the repetitions).

Algorithm \ref{alg:hash} shows the pseudocode of building a hash table
based on $SF$. $SF$ is firstly partitioned into small suffix sets by
hashing: for each suffix $suf \in SF$, its prefix $suf^{+lss}$ is
hashed to an integer $i$ between 0 and $table\_size-1$ by the string
hash function , then $suf$ is associated with the $i$-th slot of the
hash table. After that, the suffixes whose length-$lss$ prefixes are
hashed to the same value are associated with the same slot of the hash
table. Then, to address the hash collisions, for each slot that is not
$NULL$, the associated suffixes form a small suffix set $SSF$, and a
new tree node is created adaptively based on the prefix set derived
from $SSF$, as shown in the \textsf{while} loop of Algorithm
\ref{alg:amt}. The newly created tree node is then associated with the
corresponding slot of the hash table. As a result, many tree nodes
with various types can be associated with one hash table.

@@

\begin{algorithm}
  \caption{Building a hash table}\scriptsize
  \label{alg:hash}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    The suffix set $SF$ and the load factor $lf$. \\
    \ENSURE ~~\\
    The hash table.\\
    \STATE
    \STATE $ndp \leftarrow$ The number of distinct length-$lss$
    prefixes of suffixes in $SF$
    \STATE $table\_size \leftarrow \lceil ndp\,/\,lf \rceil$
    \STATE $hash\_table \leftarrow$ Create an array  of
    $table\_size$ pointers with each pointer initialized to $NULL$
    \STATE
    \FOR{each $suf \in SF$}
    \STATE $i \leftarrow Hash(suf^{+lss})$
    \STATE Associate $suf$ with $hash\_table[i]$
    \ENDFOR
    \STATE
    \FOR{$i \leftarrow 0$ to $table\_size - 1$}
    \IF{$hash\_table[i]\, \neq\, NULL$}
    \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
    \STATE $new\_node \leftarrow$ adaptively create a tree node from $SSF$, as shown in the \textsf{while} loop of Algorithm \ref{alg:amt}
    \STATE Associate $new\_node$ with $hash\_table[i]$
    \ENDIF
    \ENDFOR
    \STATE
    \RETURN $hash\_table$
  \end{algorithmic}
\end{algorithm}

In general, for a large pattern set, the root of the corresponding AMT
is usually a hash table, and the core function of the root can be
regarded as a ``filter'', which is able to filter out a great number
of positions of the text that are impossible to match any
pattern. Given a target string, the hash value of that string is
computed and used as the index of the hash table. If the corresponding
slot is $NULL$, which means the target string fails to match any key
in the hash table, the current matching round terminates and the
algorithm moves to the next position; otherwise, the process moves to
the tree node associated with that slot and compare the node with the
corresponding substring in the text.

The string hash function adopted can have a significant effect on the
performance of matching. In this work, for each matching task, the
hash function is selected randomly from a \textsf{hash function
  family} $H$, at the beginning of the matching phase. The hash
function family adopted in our implementation is the fast
\textsf{shift-add-xor} hash family proposed by Ramakrishna
\cite{Ramakrishna1997}, which is claimed to be both uniform and
universal. The form of the hash function family is shown in Algorithm
\ref{alg:hash fun}.

>>>>

\begin{enumerate}
\item Create a suffix set $SF$, and put each pattern of the pattern
  set into $SF$, where each pattern is regarded as a suffix of itself.
\item Compute the \emph{length of the shortest suffix} ($lss$) in
  $SF$. For each suffix in $SF$, remove its length-$lss$ prefix, and
  all the removed prefixes form a prefix set $PF$. Discard the
  repetitions in $PF$, and calculate $|PF|$ which refers to the
  \emph{number of distinct prefixes} ($ndp$).
\item Create a tree \emph{node} to hold the prefixes in $PF$. The
  \emph{node} is actually an index, in which each prefix serves as a
  key. The inner structure of the \emph{node} is constructed
  adaptively according to $ndp$ and $lss$ that have been computed in
  step 2.
\item Divide $SF$ by putting together all the suffixes with same
  prefix removed, to form a sub-suffix-set. Associate each
  sub-suffix-set with the corresponding prefix in the tree
  \emph{node}.
\item For each newly created sub-suffix-set in step 3, repeat the same
  procedure from step 2.
\end{enumerate}

@@

As stated in the filtering phase, once a suspicious position in the
text has been detected by the filter module, the verification module
checks that position for real pattern occurrences. Specifically, for
such a suspicious position $i$, the engine searches a sequence of
substrings of the text, where the first substring starts at $i$, in
the corresponding nodes in AMT from the root. If the text successfully
matched a key that is marked as a pattern end in some node, a pattern
is declared to be found at position $i$. However, if there is a
mismatch or the searching goes beyond the leaves of AMT, the engine
immediately forwards to the next position $i+1$ and invokes the
filter.

The pseudocode of the verification procedure is shown in Algorithm
\ref{alg:matching}. Suppose $i$ is a suspicious position in the
text. The $m\_len$ is the total length of the successfully matched
sub-strings of the text. The $node$ points to the current matching
node in the AMT. In addition, since all the keys in a node have the
same length, the notation $key\_len(node)$ is used to denote the
length of the keys in $node$.

\begin{algorithm}
  \caption{Verification}\scriptsize
  \label{alg:matching}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A suspicious position $i$ in the text $T$\\
    The AMT built from the pattern set $P$\\
    \ENSURE ~~\\
    The patterns (if any) start at $i$ 
    \STATE
    \STATE $m\_len \leftarrow 0$
    \STATE $node \leftarrow root$ of AMT
    \STATE
    \WHILE{$node \neq NULL$ and $\exists key \in node: key =
      T[i+m\_len, \, key\_len(node)]$}
    \STATE $m\_len \leftarrow m\_len + key\_len(node)$
    \IF{$key$ is marked as a pattern end}
    \STATE Report that the pattern $T[i,\,m\_len]$ is found at position $i$
    \ENDIF
    \STATE $node \leftarrow$ The child of $node.key$
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.75\textwidth]{./eps/match}
  \caption{The verification procedure for the position $i$ in the
    text.}
  \label{fig:matching}
\end{figure}

Next, an example is given in figure \ref{fig:matching} to illuminate
the verification for position $i$ of a given text string $T$, using
the AMT built in section \ref{subsec:amt}. The verification starts
from the root of AMT: according to $key\_len(root)=2$, the same length
sub-string starting at position $i$ of $T$, which is $T[i,\,2]=aa$, is
taken to check whether it's one of the keys in root. The result is:
$aa \in root$, and $aa$ is also marked as a pattern end. Therefore the
pattern $T[i,\,2]=aa$ (actually $p_6$ in $P$) is found at position
$i$. Then the verification transfers to $node_1$, which is the child
node of $root.aa$.

At $node_1$, since $key\_len(node_1)=6$, the same length sub-string
$T[i+2,\,6]=e^6$, which follows $T[i,\,2]$, is trying to match with
some key in $node_1$. The result is that: $e^6 \in node_1$ but it is
not a pattern end. Then the verification simply transfers to $node_5$,
which is the child of $node_1.e^6$.

At $node_5$, since the next sub-string $T[i+8,\,5]=u^5 \in node_5$ and
$u^5$ is marked as a pattern end, another pattern
$T[i,\,13]=a^2e^6u^5$ (actually $p_4$ in $P$) is found at position
$i$. Then the verification goes to the child of $node_5.u^5$, i.e.
$node_{10}$.

At $node_{10}$, since $T[i+13,\,4]=sscc \notin node_{10}$, the
verification for position $i$ terminates. And next, the engine will
forward to position $i+1$ and invoke the filter module for that
position.

From above it can be seen that, each verification procedure actually
corresponds to a \emph{verification path} in the AMT, whose tree nodes
have been compared with the text in the former process. In particular,
the verification path of the given example is:
$root \rightarrow node_1 \rightarrow node_5 \rightarrow node_{10}$,
witch is indicated by the dashed arrows in Figure \ref{fig:matching}.

@@

As stated in section \ref{subsec:amt}, each node of AMT has a specific
index structure to hold the prefixes of a prefix set as the keys. The
type of the index structure is chosen adaptively according to the
features of the prefix set. Since all the keys in the prefix set have
the same length, the features of the prefix set can mainly be
characterized by two values: the \emph{length} and \emph{number} of
the keys in the prefix set. These two values are respectively
symbolized by $lss$ and $ndp$ in Section \ref{subsec:amt}.

In this work, three different kinds of structures,
i.e. \emph{character map}, \emph{string array} and \emph{hash table}
can be adopted for prefix sets with different $lss$ and $ndp$
combinations. Next, the detailed descriptions of these structures will
be presented.

@@

Given a prefix set, if the length of keys is equal to 1 ($lss=1$),
i.e. each key in the prefix set is just a single character, the
space-efficient \emph{character map} structure, which was proposed by
Leis \cite{Leis2013}, will be adopted as the tree node. There are four
sub-types of character maps with different capacities for different
number of keys ($ndp$), where $1 \leq ndp \leq 256$.

@@

Figure \ref{fig:character map} illustrates the four sub-types of
character maps which are named according to their maximum
capacity. Instead of using an array of (\emph{key, child pointer})
pairs, the key part and the child pointer part are stored in the
separate arrays, which is able to keep the node structure compact
while supporting efficient search.

\begin{itemize}
\item \textbf{Map 4} (for $1 \leq ndp \leq 4$): The smallest map type
  can store up to 4 keys. It uses an array of 4 entries for keys and
  another array of the same length for child pointers. The keys and
  child pointers are stored at corresponding positions in their
  arrays, and the keys are sorted according to their ACSII
  values. Once the target string (character) is found in the key
  array, its child pointer can be located through the same position in
  the pointer array. Figure \ref{fig:character map} (a) shows a Map 4
  structure with three keys: $f$, $n$ and $p$, where the triangles
  with the keys inside represent the corresponding child nodes.

\item \textbf{Map 16} (for $5 \leq ndp \leq 16$): This map type is
  used for storing 5 to 16 keys. It has the similar structure as Map
  4, but both arrays have up to 16 entries. A target character can be
  retrieved efficiently by a binary search in the key array. Figure
  \ref{fig:character map} (b) shows a Map 16 structure with 14 keys.

\item \textbf{Map 48} (for $17 \leq ndp \leq 48$): As the number of
  keys increases, searching in the key array becomes
  expensive. Therefore, maps with more than 16 (but less than 49) keys
  do not store the keys explicitly. Instead, a 256-element \emph{index
    array} is used, which can be directly indexed by the ASCII value
  of the target character. This array stores only the array indexes
  (small inters in the range of $[0,47]$) of another pointer array
  that contains up to 48 child pointers. In this way, the storage
  space can be saved comparing with storing pointers directly, because
  each array index only requires one byte. Figure \ref{fig:character
    map} (c) shows a Map 48 structure, where the ASCII values of $a$,
  $b$ and $c$ are 97, 98 and 99 respectively.

@@

The pseudocode of searching in a node, whose type is character map, is
given in Algorithm \ref{alg:character map}.

\begin{algorithm}
  \caption{Searching in a node whose type is character map}\scriptsize
  \label{alg:character map}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is character map\\
    The target character $t\_ch$.
    \ENSURE ~~\\
    The child node of $node.t\_ch$ (possibly $NULL$).
    \STATE
    \STATE $count \leftarrow$ Number of keys in the character map
    \STATE
    \SWITCH{the sub-type of the character map}
    \CASE{\textsf{Map 4}}
    \FOR{$i \leftarrow 0$ to $count-1$}
    \IF{$keys[i]=t\_ch$}
    \RETURN $child\_pointers[i]$
    \ENDIF
    \ENDFOR
    \STATE Report a mismatch.
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 16}}
    \STATE $low \leftarrow 0, high \leftarrow count-1$
    \WHILE{$low \le high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_ch=keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_ch<keys[mid]$}
    \STATE $high \leftarrow mid-1$
    \ELSE
    \STATE $low \leftarrow mid+1$
    \ENDIF
    \ENDWHILE
    \STATE Report a mismatch.
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 48}}
    \IF{$index[t\_ch] \neq NULL$}
    \RETURN $child\_pointers[index[t\_ch]]$
    \ELSE
    \STATE Report a mismatch.
    \ENDIF
    \ENDCASE
    \STATE
    \CASE{\textsf{Map 256}}
    \RETURN $child\_pointers[t\_ch]$
    \ENDCASE
    \ENDPWITCH
  \end{algorithmic}
\end{algorithm}

@@

For the prefix set whose length of keys is greater than 1 ($lss > 1$)
and the number of keys is not greater than 100 ($ndp \leq 100$), the
\emph{string array} structure is constructed as a tree node. Similar
to the Map 4 and Map 16 structures, the keys are stored in
lexicographical order in a separate key array of $ndp \times lss$
bytes, in which each key takes $lss$ bytes. The child pointers are
stored at the corresponding positions in another pointer array. Figure
\ref{fig:string array} illustrates a string array structure holding
three keys: $aaa$, $bbb$ and $ccc$.

@@

For efficiency, if the number of keys is less than 5, a naive linear
search routine is used to search the target string in the key array;
otherwise, a more efficient (but complicated) binary search algorithm
is adopted.  The pseudocode of the searching in a node whose type is
string array is depicted in Algorithm \ref{alg:string array}, where we
use the notation $A \prec B$ to denote that string $A$ is
\emph{lexicographically smaller} than string $B$. For the string array
whose number of keys is less than 5, the target string is compared
sequentially with the keys in the key array. If the target string
matched some key, return the child pointer at the corresponding
position in the pointer array; otherwise, report a mismatch. On the
other hand, if the number of keys is greater than 4, the target string
is searched by a binary search routine from the middle element of the
key array.

\begin{algorithm}
  \caption{Searching in a node whose type is string array}\scriptsize
  \label{alg:string array}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    A tree $node$ whose type is string array; \\
    The target string $t\_str$.\\
    \ENSURE ~~\\
    The child node of $node.t\_str$ (possibly $NULL$).\\
    \STATE
    \STATE $count \leftarrow$ The number of keys in $node$
    \STATE
    \IF{$count < 5$}
    \STATE $i \leftarrow 0$
    \WHILE{$i < count$ and $keys[i] \prec t\_str$}
    \STATE $i \leftarrow i+1$
    \ENDWHILE
    \IF{$i < count$ and $keys[i]=t\_str$}
    \RETURN $child\_pointers[i]$
    \ELSE
    \STATE Report a mismatch
    \ENDIF
    \ELSE
    \STATE $low \leftarrow 0$, $high \leftarrow count-1$
    \WHILE{$low \leq high$}
    \STATE $mid \leftarrow \lfloor (low+high)/2 \rfloor$
    \IF{$t\_str = keys[mid]$}
    \RETURN $child\_pointers[mid]$
    \ELSIF{$t\_str < keys[mid]$}
    \STATE $high \leftarrow mid - 1$
    \ELSE
    \STATE $low \leftarrow mid + 1$
    \ENDIF
    \ENDWHILE
    \STATE Report a mismatch.
    \ENDIF
  \end{algorithmic}
\end{algorithm}

@@

For the prefix set whose number of keys is greater than 100 ($lss > 1$
and $ndp > 100$), searching in the string array structure becomes
inefficient even using a binary search. In this case, a more fast (but
heavy) data structure --- \emph{hash table} is adopted to deal with
large number of keys. It is worth noting that, the procedure of
building a hash table is directly based on the suffix set from which
the prefix set is formed rather than the prefix set which is the basis
of building other node structures. In this work, a hash table is an
array of child pointers with each pointer initialized to $NULL$, and
we also utilize a \emph{string hash function} which transforms a
string to a positive integer.

@@

In particular, given a suffix set $SF$, the size of the hash table
(denoted by $table\_size$) is determined by $ndp$ and a given load
factor $lf$ (ratio of $ndp$ to $table\_size$), i.e.
$table\_size = \lceil ndp\,/\,lf \rceil$. For example, with the $ndp$
of 1000 and a load factor of $70\%$, the $table\_size$ is
$\lceil 1000/0.7 \rceil = 1429$. Note that, the $ndp$ here is defined
to be the number of distinct length-$lss$ prefixes of the suffixes in
$SF$, which is equal to the size of the prefix set derived from $SF$
(after removing the repetitions).

Algorithm \ref{alg:hash} shows the pseudocode of building a hash table
based on $SF$. $SF$ is firstly partitioned into small suffix sets by
hashing: for each suffix $suf \in SF$, its prefix $suf^{+lss}$ is
hashed to an integer $i$ between 0 and $table\_size-1$ by the string
hash function , then $suf$ is associated with the $i$-th slot of the
hash table. After that, the suffixes whose length-$lss$ prefixes
hashing to the same value are associated with the same slot of the
hash table. Then, to address the hash collisions, for each slot that
is not $NULL$, the associated suffixes form a small suffix set $SSF$,
and a new tree node is created adaptively based on the prefix set
derived from $SSF$, as we have shown in the \textbf{while} loop of
Algorithm \ref{alg:amt}. The newly created tree node is then
associated with the corresponding slot of the hash table. As a result,
many tree nodes with various types can be associated within one hash
table.

@@

\begin{algorithm}
  \caption{Building a hash table}\scriptsize
  \label{alg:hash}
  \begin{algorithmic}[1]
    \REQUIRE ~~\\
    The suffix set $SF$ and the load factor $lf$. \\
    \ENSURE ~~\\
    The hash table.\\
    \STATE
    \STATE $ndp \leftarrow$ The number of distinct length-$lss$
    prefixes of suffixes in $SF$
    \STATE $table\_size \leftarrow \lceil ndp\,/\,lf \rceil$
    \STATE $hash\_table \leftarrow$ Create an array  of
    $table\_size$ pointers with each pointer initialized to $NULL$
    \STATE
    \FOR{each $suf \in SF$}
    \STATE $i \leftarrow Hash(suf^{+lss})$
    \STATE Associate $suf$ with $hash\_table[i]$
    \ENDFOR
    \STATE
    \FOR{$i \leftarrow 0$ to $table\_size - 1$}
    \IF{$hash\_table[i]\, \neq\, NULL$}
    \STATE $SSF \leftarrow \{suf\,|\,suf\in SF\; and\; Hash(suf^{+lss})=i\}$
    \STATE $new\_node \leftarrow$ adaptively create a tree node from
    $SSF$, as shown in the \textbf{while} loop of Algorithm \ref{alg:amt}
    \STATE Associate $new\_node$ with $hash\_table[i]$
    \ENDIF
    \ENDFOR
    \STATE
    \RETURN $hash\_table$
  \end{algorithmic}
\end{algorithm}

Given a target string of length $lss$, the hash value of that string
is computed and used as the index of the hash table. If the
corresponding slot is $NULL$, which means the target string fails to
match any key in the hash table, the verification terminates and the
engine moves to the next position; otherwise, the process goes to the
tree node associated with that slot and compares the node with the
corresponding substring in the text.

The string hash function adopted can have a significant effect on the
performance of verifying. In our implementation, for each matching
task, the hash function is selected randomly from a \emph{hash
  function family} $H$. The hash function family adopted in our
implementation is the fast \emph{shift-add-xor} hash family proposed
by Ramakrishna \cite{Ramakrishna1997}, which is claimed to be both
uniform and universal. The form of the hash function family is shown
in Algorithm \ref{alg:hash fun}.
